A Real-Time Sonar Simulator for Automatic Target Recognition

### 2015-10-28 Simulator/article.tex
la2pdf commit - 2015:10:27	15:59:37	(Tue27.Oct)
la2pdf commit - 2015:10:28	11:41:14	(Wed28.Oct)
la2pdf commit - 2015:10:28	19:17:10	(Wed28.Oct)
la2pdf commit - 2015:10:29	00:28:02	(Thu29.Oct)

@@

\usepackage{tikz}
\usetikzlibrary{shapes,snakes}
\usepackage{amsmath,amssymb}
% \usepackage{datatool}
% \usepackage{glossaries}

\newenvironment{outline}
{\begin{itemize}}
{\end{itemize}}

% correct bad hyphenation here
% \hyphenation{op-tical net-works semi-conduc-tor}

%%%%%%%%%%%%                                    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% GLOSSARY %
%%%%%%%%%%%%                                    ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

% \makeglossaries
% \input{../../Library/glossary}

%%%%%%%%%%%%%%%%%%                              ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
% DOCUMENT START %
%%%%%%%%%%%%%%%%%%                              ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

% \usepackage{yfonts}

% \graphicspath{submission/final/gfx/}

@@

\maketitle

@@

@@

\begin{figure}[t]\centering%
\graphicsAI[width=\linewidth]{gfx/scene_photograph.svg}%
\caption{Simulator principle.}\label{simulator_principe}%
\end{figure}

\begin{figure}[t]\centering%
\graphicsAI[drawing,width=\linewidth]{gfx/specs.svg}%
\caption{Simulator specifications.}\label{specs}%
\end{figure}

@@

We implement rotations in a 3D euclidean space by combining matrices that rotate around each of the three respective dimensions.. For rotation by an angle $\phi_x$ clockwise around the $x$-axis we have
\begin{align}
\R_x(\phi_x) &= \bmat{
1  &  0           &  0           &  0 \\
0  &  \cos\phi_x  &  -\sin\phi_x &  0 \\
0  &  \sin\phi_x  &  \cos\phi_x  &  0 \\
0  &  0           &  0           &  1 \\
},
\end{align}
and similarly, for the other two euclidean dimensions we have
\begin{align}
\R_y(\phi_y) &= \bmat{
\cos\phi_y  &  0  &  \sin\phi_y  &  0 \\
0           &  1  &  0           &  0 \\
-\sin\phi_y &  0  &  \cos\phi_y  &  0 \\
0           &  0  &  0           &  1 \\
},
\end{align}
and
\begin{align}
\R_z(\phi_z) &= \bmat{
\cos\phi_z  &  -\sin\phi_z &  0  &  0 \\
\sin\phi_z  &  \cos\phi_z  &  0  &  0 \\
0           &  0           &  1  &  0 \\
0           &  0           &  0  &  1 \\
}.
\end{align}
The order in which these are applied matters. We rotate around the $x$-axis first, then around $y$ and finally around $z$:
\begin{align}
\R(\phi_x, \phi_y, \phi_z) &= \R_z(\phi_z)\;\R_y(\phi_y)\;\R_x(\phi_x).
\end{align}

>>>>

\newif\ifBuildBibliography\BuildBibliographyfalse  % Whether to include the references.bib file or use inline references.

@@

\newcommand\minus{\scalebox{0.75}[1.0]{$-$}}

% \usepackage{tikz}
% \usetikzlibrary{shapes,snakes}
\usepackage{amsmath,amssymb}
% \usepackage{datatool}
% \usepackage{glossaries}

% \newenvironment{outline}
% {\begin{itemize}}
% {\end{itemize}}

@@

@@

\setcounter{totalnumber}{1}
\setcounter{topnumber}{1}
\setcounter{dbltopnumber}{1}

\begin{figure*}[t]\centering%
\graphicsAI[width=\linewidth]{gfx/scene_coordinate_system.svg}%
\caption{Simulator principle.}\label{simulator_coordinate_system}%
\end{figure*}

% \begin{figure}[t!]\centering%
% \graphicsAI[drawing,width=\linewidth]{gfx/specs.svg}%
% \caption{Simulator specifications.}\label{specs}%
% \end{figure}

@@

@@

We implement rotations in a 3D euclidean space by combining matrices that rotate around each of the three respective dimensions. For rotation by an angle $\phi_x$ clockwise around the $x$-axis we have
\begin{align}
\R_x(\phi_x) &= \bmat{
1  &  0           &  0           &  0 \\
0  &  \cos\phi_x  &  -\sin\phi_x &  0 \\
0  &  \sin\phi_x  &  \cos\phi_x  &  0 \\
0  &  0           &  0           &  1 \\
},
\end{align}
and similarly, for the other two euclidean dimensions we have
\begin{align}
\R_y(\phi_y) &= \bmat{
\cos\phi_y  &  0  &  \sin\phi_y  &  0 \\
0           &  1  &  0           &  0 \\
-\sin\phi_y &  0  &  \cos\phi_y  &  0 \\
0           &  0  &  0           &  1 \\
},
\end{align}
and
\begin{align}
\R_z(\phi_z) &= \bmat{
\cos\phi_z  &  -\sin\phi_z &  0  &  0 \\
\sin\phi_z  &  \cos\phi_z  &  0  &  0 \\
0           &  0           &  1  &  0 \\
0           &  0           &  0  &  1 \\
}.
\end{align}
The order in which these are applied matters. We rotate around the $x$-axis first, then around $y$ and finally around $z$:
\begin{align}
\R(\phi_x, \phi_y, \phi_z) &= \R_z(\phi_z)\;\R_y(\phi_y)\;\R_x(\phi_x).
\end{align}
